Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-12 doc/JFLA2022/paper.tex
Include a paragraph on Docker-Coq-Action, expand comparison with Nix-based CI.

\paragraph{The Dune build system}
It allows building packages contained in a single source tree separately, which is essential to be able to publish the different libraries contained in a single repository as separate (opam) packages to the Coq package index.

@@

\paragraph{The Coq Nix Toolbox~\cite{cohen:hal-03366644}}
We rely on this toolbox mainly because it can generate a Continuous Integration setup (relying on GitHub Actions) to test the various libraries contained in the project, but also their dependencies.
%
This has allowed us, for instance, to test the Goedel library with the current version of the Hydra-battles library when we have moved a subpart of Goedel to Hydra-battles (the Ackermann sub-library).

The built artifacts are stored in the \community binary cache on Cachix~\cite{cachix}.
%
This means that a given version never has to be built twice and Continuous Integration can be almost instantaneous when no change has been made (e.g., after merging a pull request).

>>>>

\paragraph{The Dune build system~\cite{dune}}
This build system, originally written for OCaml, but that was extended to support Coq projects, allows building packages contained in a single source tree separately, which is essential to be able to publish the different libraries contained in a single repository as separate (opam) packages to the Coq package index.

@@

\paragraph{The Docker-Coq-Action~\cite{martindorel2020dockercoq}}
This GitHub Action provides a very simple way of setting up Continuous Integration (CI) for a Coq project with an opam file.
%
At the current time, we rely on it, together with the mathcomp Docker images~\cite{mathcompdocker}, to test our two main libraries, Hydra-battles and Addition-chains, with multiple versions of Coq.

\paragraph{The Coq Nix Toolbox~\cite{cohen:hal-03366644}}
This toolbox, based on the Nix package manager, provides an alternative way of setting up CI for a Coq project (also relying on GitHub Actions).
%
We use this Nix-based CI for several things.

\begin{enumerate}
\item To test the build of the project (as a single unit) with coq\_makefile (whereas the Docker-based CI relies on the opam packages, which use Dune to build the libraries contained in the project).

\item To generate the documentation of the project (book in PDF format and coqdoc HTML pages) by relying on the output of the coq\_makefile build.

\item To test the bridge to the Gaia library, because the Nix-based CI supports out-of-the-box caching of build dependencies.
%
Given that Gaia takes more than 5 minutes to build, this build is only done once, then reused at each new run of the CI.

\item To test compatibility with the Goedel library, which was made to depend on the Hydra-battles library since the Ackermann sub-library was moved from the former to the latter.
%
For this, we rely on the fact that the Coq Nix Toolbox has native support for generating a CI configuration that includes reverse dependency compatibility testing.
\end{enumerate}

The artifacts of the Nix builds are stored in the \community binary cache on Cachix~\cite{cachix}.
%
This means that a given version never has to be built twice and Continuous Integration can be almost instantaneous when no change has been made (e.g., after merging a pull request).

By relying on two different technologies for CI, we are able to fit a larger range of use cases, while also providing more assurance that the project does build correctly in a variety of configurations.
%
Given that the two technologies are well maintained (within \community), relying on both does not incur a significant cost, compared to the benefits they provide.
